---
title: "TidyTuesdays with X-MEN"
description: |
  Working on X-MEN Dataset with Tidyverse
author: Rohan Kataria
date: 07-22-2020
categories:
  - Everyday Programming
  - Tidyverse
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
## Introduction
## Motivation
## Diving into the Dataset

### Getting Data and Libraries
```{r loading_data, eval=FALSE, echo=TRUE}
#Laoding  Required Libraries
library(tidyverse)
theme_set(theme_light())

#Laoding Data in character_visualization
character_visualization <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-06-30/character_visualization.csv')

```

### What is there in Data?
```{r data_summary}
library(DT)
character_visualization <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-06-30/character_visualization.csv')
datatable(character_visualization, options = list(
  pageLength = 5
  ))
```

### Cleaning Data
I definitely want to see Superhero and their Secret Identities separate. 
```{r cleaning_data, eval=FALSE, echo=TRUE}
character_visualization <- character_visualization %>%
  separate(character, c("superhero", "secret_identity"), sep= " = ", fill = "right")
```

```{r cleaned_data}
library(DT)
library(tidyverse)

character_visualization <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-06-30/character_visualization.csv') %>%
  separate(character, c("superhero", "secret_identity"), sep= " = ", fill = "right")

datatable(character_visualization, options = list(
  pageLength = 5
  ))

```

### How many issues are there in the Data?
Answer is 50
```{r eval=FALSE, echo=TRUE}
character_visualization %>%
  count(issue) %>%
```

```{r}
character_visualization %>%
  count(issue)
```

### How many Superheroes are there?
Answer is 25, considering since Superhero is once inside Costume and out of Costume.
```{r eval=FALSE, echo=TRUE}
character_visualization %>%
  count(superhero, costume) %>%
  datatable()
```

```{r}
character_visualization %>%
  count(superhero, costume) %>%
  datatable()
```

### Which X-Men speak in the most issues?

```{r eval=FALSE, echo=TRUE}
#Creating dataset by_character to 
by_character <- character_visualization %>%
  group_by(superhero) %>%
  summarise(
    across(speech:depicted,
           list(total = sum,
                issues = ~sum(.>0),
                avg = ~ mean(.[depicted > 0])))) 


by_character %>%
  arrange(desc(speech_issues)) %>%
  filter(speech_issues > 0) %>%
  head(20) %>%
  mutate(superhero = fct_reorder(superhero, speech_issues)) %>%
  ggplot(aes(speech_issues, superhero)) + 
  geom_col() + 
  labs(title = "Which X-men speak in the most issues?",
       x = "# of issues",
       y = "")

```

```{r xmen_speak}
by_character <- character_visualization %>%
  group_by(superhero) %>%
  summarise(
    across(speech:depicted,
           list(total = sum,
                issues = ~sum(.>0),
                avg = ~ mean(.[depicted > 0])))) 


by_character %>%
  arrange(desc(speech_issues)) %>%
  filter(speech_issues > 0) %>%
  head(20) %>%
  mutate(superhero = fct_reorder(superhero, speech_issues)) %>%
  ggplot(aes(speech_issues, superhero)) + 
  geom_col() + 
  labs(title = "Which X-men speak in the most issues?",
       x = "# of issues",
       y = "")
```

### Avg lines per issue depicted
```{r eval=FALSE, echo=TRUE}
library(ggrepel)

#Finding out Issues vs Avg Lines
#Here we are looking for how often they appear(depict) vs Speech
by_character %>%
  ggplot(aes(depicted_issues, speech_avg)) +
  geom_point() +
  geom_text_repel(aes(label = superhero)) +
  labs(title = "Average Lines Per issue?",
      x = "# of issues in which character appears",
       y = "Avg lines per issue depicted") +
  expand_limits(y = 0)
```

```{r}
library(ggrepel)

#Finding out Issues vs Avg Lines
#Here we are looking for how often they appear(depict) vs Speech
by_character %>%
  ggplot(aes(depicted_issues, speech_avg)) +
  geom_point() +
  geom_text_repel(aes(label = superhero)) +
  labs(title = "Average Lines Per issue?",
      x = "# of issues in which character appears",
       y = "Avg lines per issue depicted") +
  expand_limits(y = 0)
```

### How often they get thoughts?
```{r eval=FALSE, echo=TRUE}
by_character %>%
  ggplot(aes(depicted_issues, thought_avg)) +
  geom_point() +
  geom_text_repel(aes(label = superhero)) +
  labs(title = "Thoughts they get in each issue?",
       x = "# of issues",
       y = "Avg thoughts per issue") +
  expand_limits(y = 0)
```

```{r}
by_character %>%
  ggplot(aes(depicted_issues, thought_avg)) +
  geom_point() +
  geom_text_repel(aes(label = superhero)) +
  labs(title = "Thoughts they get in each issue?",
       x = "# of issues",
       y = "Avg thoughts per issue") +
  expand_limits(y = 0)
```

### Which Charachters can think, Which Speak?
```{r eval=FALSE, echo=TRUE}
by_character %>%
  ggplot(aes(depicted_issues, speech_avg/ thought_avg)) +
  geom_point() +
  geom_text_repel(aes(label = superhero)) +
  expand_limits(y = 1) +
  scale_y_log10(breaks = c(1,3,10,30),
                labels = c("Same", "3X", "10X", "30X")) +
  labs(x = "# of issues depicted",
       y = "Speech to thought ration (log scale)",
       title = "Which Charachters can think, Which Speak?")

```

```{r}
by_character %>%
  ggplot(aes(depicted_issues, speech_avg/ thought_avg)) +
  geom_point() +
  geom_text_repel(aes(label = superhero)) +
  expand_limits(y = 1) +
  scale_y_log10(breaks = c(1,3,10,30),
                labels = c("Same", "3X", "10X", "30X")) +
  labs(x = "# of issues depicted",
       y = "Speech to thought ration (log scale)",
       title = "Which Charachters can think, Which Speak?")
```

### Does the speak/thought pattern change with costume?

```{r eval=FALSE, echo=TRUE}
#Doing same aggregation as above, but grouping by superhero and costume
#below is the new aggregation, new aggregations possible for new questions
by_character_costume <- character_visualization %>%
  group_by(superhero, costume) %>%
  summarize(across(speech:depicted,
                   list(total = sum,
                        issues = ~ sum(. > 0),
                        avg = ~ mean(.[depicted > 0])))) %>%
  ungroup() %>% #Ungrouping else it will still remain grouped as superhero
  mutate(speech_thought_ratio = speech_avg / thought_avg) #taking speech thought avg ratio

#PIVOTING Data
#fct_reorder reorders x on basis of y. reorders one variable by another.
by_character_costume %>%
  mutate(superhero = fct_reorder(superhero, speech_total)) %>%
  filter(speech_avg > 0) %>%
  ggplot(aes(speech_total,
             superhero,
             color = costume,
             size = depicted_issues)) +
  geom_point() +
  labs(x = "# of lines (in/out of costume)")
```

```{r}
#Doing same aggregation as above, but grouping by superhero and costume
#below is the new aggregation, new aggregations possible for new questions
by_character_costume <- character_visualization %>%
  group_by(superhero, costume) %>%
  summarize(across(speech:depicted,
                   list(total = sum,
                        issues = ~ sum(. > 0),
                        avg = ~ mean(.[depicted > 0])))) %>%
  ungroup() %>% #Ungrouping else it will still remain grouped as superhero
  mutate(speech_thought_ratio = speech_avg / thought_avg) #taking speech thought avg ratio

#PIVOTING Data
#fct_reorder reorders x on basis of y. reorders one variable by another.
by_character_costume %>%
  mutate(superhero = fct_reorder(superhero, speech_total)) %>%
  filter(speech_avg > 0) %>%
  ggplot(aes(speech_total,
             superhero,
             color = costume,
             size = depicted_issues)) +
  geom_point() +
  labs(x = "# of lines (in/out of costume)")

```


### Whos is more in costume by the number of lines?
Gambit is always in costume, Professor X is never in costume. Storm's half the dialogs are in costume.

```{r eval=FALSE, echo=TRUE}
library(ggrepel)

costume_ratios <- by_character_costume %>%
  filter(speech_avg > 0) %>%
  group_by(superhero) %>%
  summarize(costume_ratio = speech_total[1] / speech_total[2]) %>%
  inner_join(by_character, by = "superhero") #inner joining by previously creating dataset on superhero

costume_ratios %>%
  ggplot(aes(speech_total,
             costume_ratio)) +
  geom_point() +
  geom_text_repel(aes(label = superhero)) +
  scale_y_log10() +
  labs(x = "Total # of lines",
       y = "Lines in costume / lines out of costume")
```

```{r}
library(ggrepel)

costume_ratios <- by_character_costume %>%
  filter(speech_avg > 0) %>%
  group_by(superhero) %>%
  summarize(costume_ratio = speech_total[1] / speech_total[2]) %>%
  inner_join(by_character, by = "superhero") #inner joining by previously creating dataset on superhero

costume_ratios %>%
  ggplot(aes(speech_total,
             costume_ratio)) +
  geom_point() +
  geom_text_repel(aes(label = superhero)) +
  scale_y_log10() +
  labs(x = "Total # of lines",
       y = "Lines in costume / lines out of costume")

```

### Which X-Men tend to speak in costume/out of costume?
We can also answer the last quesiton in a different way, and find out a ratio of Speaking inside costume and outside using Lolipop Graph. The Lolipop graph is a great way to tell in which direction the ratio goes. For example: following graph tells us Wolverine had a lot of lines and he speaks mosty inside costume.

```{r eval=FALSE, echo=TRUE}
costume_ratios %>%
  mutate(superhero = fct_reorder(superhero, costume_ratio)) %>%
  ggplot(aes(costume_ratio, y = superhero)) +
  geom_errorbarh(aes(xmin = 1, xmax = costume_ratio), height = 0) + #1 is the starting point
  geom_point(aes(size = speech_total, color = costume_ratio > 1)) +
  scale_x_log10() +
  scale_color_discrete(guide = FALSE) +
  labs(size ="# of lines",
       x = "Lines in costume / lines out of costume",
       y = "",
       title = "Which X-Men tend to speak in costume/out of costume?")
```


```{r}
costume_ratios %>%
  mutate(superhero = fct_reorder(superhero, costume_ratio)) %>%
  ggplot(aes(costume_ratio, y = superhero)) +
  geom_errorbarh(aes(xmin = 1, xmax = costume_ratio), height = 0) + #1 is the starting point
  geom_point(aes(size = speech_total, color = costume_ratio > 1)) +
  scale_x_log10() +
  scale_color_discrete(guide = FALSE) +
  labs(size ="# of lines",
       x = "Lines in costume / lines out of costume",
       y = "",
       title = "Which X-Men tend to speak in costume/out of costume?")
```

## What did I learn?
1. Data Manupulating in Tidyverse and Visualising in GGPLOT2 is like writing a sentence in Plain English. Hands Down!

2. EDA is proportional to the level of curiosity.

3. Lolipop Chart makes easier to visualise ratios. 

4. Across Feature lets you apply a function (or a set of functions) to a set of columns. (This was new to me)