---
title: "Storing API Data in a Database"
description: |
  Learn how to store API data in your database
author:
  - name: Rohan Kataria
    url: {}
date: 07-11-2020
categories:
  - database
preview: images/preview.jpg
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
    self_contained: false
---
## Introduction
API allows a user to request data straight from a website. Instead of having to download a dataset, you could load it in your console with just a link. (Less Messy Desktop!!) Look here for [Public APIs](https://github.com/public-apis/public-apis#index).
Today we will talk about pulling data for your data project using an API and storing the data in your database. Yes! You don't have to maintain any file on your desktop.

## Getting API data in R
Super easy when we want to read a csv file, but when we have to get the API data in our console, we need to install R's **Jsonlite package**. 

I have used [CHRONICLING AMERICA's](https://chroniclingamerica.loc.gov/) public api for this demo.

```{r api_data, eval=FALSE, echo=TRUE}
library(jsonlite)
data_web <- fromJSON("https://chroniclingamerica.loc.gov/suggest/titles/?q=Massachusetts")
data <- as.data.frame(data_web)
```

## Storing API data in PostgreSQL
For this operation, we need to install **RPostgreSQL** package.

*More about this package [can be found here.](https://cran.r-project.org/web/packages/RPostgreSQL/index.html)*

```{r postgresql, eval=FALSE, echo=TRUE}
#Loading required libraries
library(RPostgreSQL)
library(DBI)
library(odbc)

#Credentials
pw = 'Your Password'
drv = dbDriver("PostgreSQL")
con = dbConnect(drv, dbname = "Your Database Name",
                host = "Your Host", port = 5432,
                user = "Your User", password = pw)

#Injecting Data in Table
dbWriteTable(con, "TableName", 
             value = data, append = TRUE, row.names = FALSE)
```

## Sotring API data in MongoDB
For this operation, we need to install **Mongolite** package.

*More about this package [can be found here.](https://cran.r-project.org/web/packages/mongolite/index.html)*

```{r mongodb, eval=FALSE, echo=TRUE}
#Loading required libraries
library(mongolite)

#Credentials
mongo_db_user <- "Your User"
mongo_db_password <- "Your password"
mongo_database <- "Your Database"
mongo_collection <- "Collection Name"
mongo_clustername <- "Your Cluster Link"

url_path = sprintf("mongodb+srv://%s:%s@%s/admin",
                   mongo_db_user, mongo_db_password, mongo_clustername)
mongo_db <- mongo(collection = mongo_collection, db = mongo_database, url = url_path, verbose = TRUE)

#Injecting Data in Collection
mongo_db$insert(data_web)

```

## Conclusion
API and Cloud Databases together are a great option to run a project online/on the web. Not just both saves space and memory of your local machine but also gives you a better opportunity to scale and deploy your project into an application and show it to the world.
